The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-10-03 paper/Analisis.tex
More text in off-center emission specialy in the angular dependency part

As we know there is unlikely to find galaxies with radiation sources 
distributed homogeneously. Most of them are in a clumpy distribution 
(Laursen et al 2013*) which affected the resulting spectra. In order 
to study an inhomogeneous distribution we set up a model in which we 
select certain photons that are placed in a specific place but that 
are not symmetrically distributed Fig. \ref{fig:OCspheres} shows the distributions we 
set up, basically we take photons located in a sphere of $0.5 R$ and 
we choose two speheres in each side of the $\hat{\textbf{x}}$ axis
two at $0.25 R$ and the other two at $0.5 R$

@@

As a primer approach we study the angular dependency in the same manner as
we do in section(). In Fig. \ref{fig:OCflux} the angular for two different
off-center distribution the bold line shows an off center sphere located
at $0.5 R$ of the homogeneous sphere, while the narrow line shows sphere 
located at $0.25 R$. This is done for the model with $\tau=10^{5}$ and 
$V=50 km s^{-1}$, we find that the maximum change in flux would be up to.

@@

The outgoing spectra for two different spheres located at $-0.25R$ and $0.25R$ respectively
is shown in Fig. \ref{fig:OCspectra}, we have shown this positions because
they are the most sensitive to rotational velocities.
\begin{figure}
\includegraphics[scale=0.3]{OC_5t_vel100.jpg}
\caption{Spectra for two off-center spheres
   \label{fig:OCspectra}} 
\end{figure}

There are two new morphological featueres that off-center emission in 
rotating galaxies produces. First in some of our models with especific 
values of velocity and opitcal depth an asymmetry in the peak heights 
is presented, those off-center spheres \textit{(put image reference)} 
located at the positive side of $\hat{\textbf{x}}$ in Fig.\ref{fig:OCspheres}
present a higher peak in the redshifted part, while those spheres located
at the negative side of $\hat{\textbf{x}}$ present a higher blue shifted peak,
we found that the higher asymmetry is for model with $\tau=10^7, V=200 kms^{-1}$ where one peak is $20\%$ higher than the other.
This can be apreciated for both set of spheres at $0.25 R$ and $0.5 R$,
 but the effect shows a stronger asymmetry for spheres located at $0.25 R$
 this due to the fact that photons escaping from this spheres goes through 
 a larger hidrogen medium than photons located in the spheres at $0.5 R$.
%poner valores de velocidad y optical depth porcentaje de asimetria

@@

Group III profiles are better represented by galaxies rotating at $V > 100 kms^{-1}$\\
... Comparison with Verhamme et al. results on the rotation (Viewing angle)

@@

%ideas:
Keep in mind making a follow up paper on the results of Yamada et atl
http://adsabs.harvard.edu/abs/2012ApJ...751...29Y on the line
morphology at z=3.1. How many of t hese laes can be considered to have
rotation features? In principle, all of then should have them. How to
make the case convincing in the statistical sense?

>>>>

As we know there is unlikely to find galaxies with radiation sources 
distributed homogeneously. Most of them are in a clumpy distribution 
(Laursen et al 2013*) which affected the resulting spectra. In order 
to study an inhomogeneous distribution we set up a model in which we 
select certain photons that are placed in a specific place but that 
are not symmetrically distributed Fig. \ref{fig:OCspheres} shows the distributions we 
set up, basically we take photons located in a sphere of $0.5 R$ where
$R$ is the radii of the homogeneous sphere and 
we choose two spheres in each side of the $\hat{\textbf{x}}$ axis
two at $0.25 R$ and the other two at $0.5 R$.

@@

As a primer approach we study the angular dependency in the same manner as
we do in section \ref{sec:results}, but with the set up of the off-center models
where the galaxy is rotating around the  $\hat{\textbf{z}}$ axis,  the observer is 
located at . In Fig. \ref{fig:OCflux} the angular 
dependency for two different off-center distribution are shown. the bold line  
represents an off center sphere located at $0.25 R$ in the homogeneous sphere, while 
the narrow line shows a sphere located at $-0.25 R$. This is done for the model 
with $\tau=10^{5}$ and $V=50 km s^{-1}$, but results with the rest of models
show exactly the same trend. We find a high dependency in the viewing angle,
in particular observers at .

@@

The outgoing spectra for two different spheres located at $-0.25R$ and $0.25R$ respectively
are shown in Fig. \ref{fig:OCspectra}, we have shown this positions because
they are most sensitive to the effect of rotation.

\begin{figure}
\includegraphics[scale=0.3]{OC_5t_vel100.jpg}
\caption{Spectra for two off-center spheres
   \label{fig:OCspectra}} 
\end{figure}

There are two new morphological features that off-center emission in 
rotating galaxies produces. First in some of our models with specific 
values of velocity and optical depth an asymmetry in the peak heights 
is presented, those off-center spheres \textit{(put image reference)} 
located at the positive side of $\hat{\textbf{x}}$ in Fig.\ref{fig:OCspheres}
present a higher peak in the redshifted part, while those spheres located
at the negative side of $\hat{\textbf{x}}$ present a higher blue shifted peak,
we found that the higher asymmetry is for model with $\tau=10^7, V=200 kms^{-1}$ where one peak is $20\%$ higher than the other.

This can be appreciated for both set of spheres at $0.25 R$ and $0.5 R$,
 but the effect shows a stronger asymmetry for spheres located at $0.25 R$
 this due to the fact that photons escaping from this spheres goes through 
 a larger hydrogen medium than photons located in the spheres at $0.5 R$.
%poner valores de velocidad y optical depth porcentaje de asimetria

@@

Group III profiles are better represented by galaxies rotating at $V > 100 kms^{-1}$\\

... Comparison with Verhamme et al. results on the rotation (Viewing angle)

@@

%ideas:
Keep in mind making a follow up paper on the results of Yamada et al
http://adsabs.harvard.edu/abs/2012ApJ...751...29Y on the line
morphology at z=3.1. How many of these laes can be considered to have
rotation features? In principle, all of then should have them. How to
make the case convincing in the statistical sense?
